My title

### 2024-02-15 outputs/paper/paper.qmd
finished result

# Results

```{r}
#| label: fig-Composite-Search-Intensity 
#| fig-cap: Composite-Search-Intensity both type
#| warning: false
#| message: false
#| echo: false

# plot graphs
library(ggplot2)
library(dplyr)

bully_data <- subset(bully_clean_data, bully_type == "sch_cyb_bully")

@@

# plot from "bullying" data
ggplot(bully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
  geom_line() +
  ggtitle("Composite Search Intensity for School Bullying and Cyberbullying") +
  xlab("Date") +
  ylab("Search Intensity") +
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
             linetype = "dashed", color = "red")+
   scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
               date_labels = "%Y-%m", 
               limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
#| label: fig-Composite-Search-Intensity-school
#| fig-cap: Composite-Search-Intensity school type
#| warning: false
#| message: false
#| echo: false
# plot from "school bullying" data
ggplot(schbully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
  geom_line() +
  ggtitle("Composite Search Intensity for School Bullying") +
  xlab("Date") +
  ylab("Search Intensity") +
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
             linetype = "dashed", color = "red")+
  scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
               date_labels = "%Y-%m", 
               limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
#| label: fig-Composite-Search-Intensity-cyber
#| fig-cap: Composite-Search-Intensity cyber type
#| warning: false
#| message: false
#| echo: false
# plot from "cyberbullying" data
ggplot(cyberbully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
  geom_line() +
  ggtitle("Composite Search Intensity forCyberbullying") +
  xlab("Date") +
  ylab("Search Intensity") +
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
             linetype = "dashed", color = "red")+
  scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
               date_labels = "%Y-%m", 
               limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

 The data presented in @fig-Composite-Search-Intensity provides valuable insights into the trends of searches from 2012 to 2021. The observed pattern, with peaks of bullying during the first month of school and troughs in the summer, suggests a recurring seasonal variation in the interest or concern about bullying . This cyclic behavior aligns with the typical school calendar, highlighting a potential correlation between the academic year's start and increased awareness or experiences related to bullying.

@@

>>>>

# Results
```{r}
#| label: tbl-Search-Intensity
#| tbl-cap:  Table-of-Search-Intensity by School Bullying and Cyber Bullying
#| warning: false
#| message: false
#| echo: false
knitr::kable(head(bully_clean_data),'markdown',col.names = c("US State", "Date", "Number of Searches", "Bully Type"),align = 'c',

                      caption = "Sample Table for Search Intensity by School Bullying and Cyber Bullying (2012-2021)")
```

```{r}
#| label: fig-Composite-Search-Intensity-bully
#| fig-cap: Composite-Search-Intensity by School Bullying and Cyber Bullying
#| warning: false
#| message: false
#| echo: false

# plot graphs
bully_data <- subset(bully_clean_data, bully_type == "sch_cyb_bully")

@@

# plot from "bullying" data
ggplot(bully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
  geom_line() +
  xlab("Date") +
  ylab("Search Intensity") +
   labs(title = "Composite-Search-Intensity by School and Cyber Bullying")+
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
             linetype = "dashed", color = "red")+
   scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
               date_labels = "%Y-%m", 
               limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
#| label: fig-Composite-Search-Intensity-school
#| fig-cap: Composite-Search-Intensity school type
#| warning: false
#| message: false
#| echo: false
# plot from "school bullying" data
ggplot(schbully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
  geom_line() +
  xlab("Date") +
  ylab("Search Intensity") +
   labs(title = "Composite-Search-Intensity by School Bullying")+
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
             linetype = "dashed", color = "red")+
  scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
               date_labels = "%Y-%m", 
               limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
#| label: fig-Composite-Search-Intensity-cyber
#| fig-cap: Composite-Search-Intensity cyber type
#| warning: false
#| message: false
#| echo: false
# plot from "cyberbullying" data
ggplot(cyberbully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
  geom_line() +
  xlab("Date") +
  ylab("Search Intensity") +
     labs(title = "Composite-Search-Intensity by Cyber Bullying")+
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
             linetype = "dashed", color = "red")+
  scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
               date_labels = "%Y-%m", 
               limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

The dataset represented by the table labeled @tbl-Search-Intensity furnishes a comprehensive overview of the cumulative number of searches related to bullying over the specified time frame. This table is a valuable resource for conducting a nuanced analysis, as it delineates key variables crucial for understanding the extent of harm experienced by individuals affected by bullying. The primary variables include time, state, the total number of searches, and the categorization of bullying incidents. The categorization of bullying incidents into different categories provides a nuanced understanding of the multifaceted nature of bullying. By disaggregating searches based on bullying categories, such as traditional bullying and cyberbullying, analysts can discern which forms of bullying are more prevalent or garner more attention during specific time periods and in particular states.

In essence, the @tbl-Search-Intensity table serves as a rich repository of information, offering a multifaceted perspective on the harm suffered by individuals affected by bullying. Researchers can leverage this dataset to uncover temporal trends, regional variations, and category-specific nuances, ultimately contributing to a more comprehensive and targeted approach in addressing the complex issue of bullying.

The data presented in @fig-Composite-Search-Intensity-bully provides valuable insights into the trends of searches from 2012 to 2021. The observed pattern, with peaks of bullying during the first month of school and troughs in the summer, suggests a recurring seasonal variation in the interest or concern about bullying . This cyclic behavior aligns with the typical school calendar, highlighting a potential correlation between the academic year's start and increased awareness or experiences related to bullying.

@@

The two-dimensional analysis of bullying searches, as depicted in @fig-Number-of-Searches-represented-by-point-size, offers valuable insights into the regional variations and the overall prevalence of bullying concerns. By juxtaposing the number of bullying searches in specific states with the nationwide search volume, a nuanced understanding of the relative intensity of bullying-related issues emerges. The substantial discrepancy between the search volumes for bullying in New York State and New Jersey, with New York registering nearly twice the number of searches, underscores the regional disparities in the perception or awareness of bullying. This contrast could be influenced by a myriad of factors, such as differences in population density, educational policies, cultural dynamics, or varying levels of community engagement in anti-bullying initiatives. The elevated search volume in New York may suggest a higher incidence of bullying incidents or a greater public awareness and sensitivity to the issue. This heightened attention could be attributed to proactive anti-bullying campaigns, robust educational programs, or a more open dialogue surrounding the topic within the state. Conversely, the comparatively lower search volume in New Jersey may indicate a different set of contextual factors influencing the perception and reporting of bullying. The two-dimensional analysis not only provides insights into state-level variations but also allows for a comparison with the nationwide search volume. Understanding how specific states compare to the national average in terms of bullying searches can highlight regions where the issue is particularly salient or, conversely, where it may be relatively underreported or less prevalent. The two-dimensional analysis of bullying searches based on the number of state and nationwide searches reveals a nuanced landscape of regional variations in the perception and awareness of bullying. The disparities observed in Figure 4 provide a starting point for further investigations and interventions to address the complex and multifaceted nature of bullying at both the state and national levels.
